Augmenting the DonorsChoose.org Corpus for Meta-Learning

### 2019-04-10 doc/paper/main.tex
paper/main.tex: Empty page style
Get rid of an annoying chapter hint in the header by switching to a
blank page style using `\pagestyle`. Comment out `\makeboth`
accordingly and add a note.
{paper,poster}/main.tex: Tweaks and suggestions

	\lstset{basicstyle=\ttfamily,breaklines=true}  % Prettier code highlighting style
	\pagestyle{myheadings}  % Prettier page format with header but without footer

@@

\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}}
\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2} \and Joeran~Beel\inst{1,2}}
\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
\institute{
	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, collinsa@tcd.ie, aizawa@nii.ac.jp}
}

\maketitle  % Typeset the header of the contribution
\markboth{}{}  % Clear the section and author from the page header

@@

Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way as to allow researchers to focus on the actual meta-learning task. We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich and vast corpus is a suitable candidate. The raw dataset is augmented with metadata of several machine learning algorithms from a variety of fields (cf.~\cite{DBLP:journals/corr/abs-1805-12118}). In place of a metric, the recall in a Top-N set is used as it can be computed for a wide range of algorithms. The dataset is further amended with aggregated statistics about users and items, and metadata of an exemplary experiment.

@@

\subsection{The Dataset}
DonorsChoose.org is an organization which enables teachers to file project requests for resources for their school. Collectively the nonprofit has raised $\$685$ million for classrooms in the United States of America. Their dataset composed of past donations features $4.69$ million transactions performed by $2.12$ million users having donated to $1.11$ million projects. The corpus provides significantly more transactions with more detailed item and transaction information compared to, e.g., the popular MovieLens dataset. An exemplary itemized view of the augmented dataset is shown in~\autoref{tab:IllustrativeTable}.

@@

In a first step, two collaborative filtering techniques and two content-based filtering techniques are applied. The performance measures of the single algorithms are amended to the table. Next, aggregated user and item statistics are calculated and added to the table. Lastly, four exemplary meta-learners are applied and the performance measures of the individual approaches are added to the corpus.

@@

Additionally, users having interacted less than twice are removed as well. Although, this limits the target group, the step is unavoidable as the employed validation process requires at least one interaction per user for testing and one for training. The evaluation requires user profiles and hence training-transactions in order to recommend new items which in turn need to be validated against test-transactions. Lastly, the donated amount is transformed to a transaction strength in the range of unity to five in analogy to a rating score. This step reduces the influence of outliers respectively uncommon donated amounts.

@@

The recall in a Top-N test set is used as score of how good an algorithm is able to recommend an item.
\begin{enumerate*}[label= (\arabic*)]
	\item For each user, first $100$ items with which the user has not interacted with are selected.
	\item The algorithm is then requested to rank an item with which the user has interacted with but which was not used for building the user's profile and the $100$ randomly sampled items. It is assumed that the random $100$ items are of low interest to the user.
	\item The position of the item with which the user has interacted with in the ranked test set may now be taken as the recall in a Top-N test set.
\end{enumerate*}

@@

\subsection{Statistics and Application of Learning Subsystem}
The meta-learning system processes the metadata of the learning subsystem and further statistics. Its performance is evaluated via a holdout split on the transaction table using $80\%$ for training and the rest for testing. Transactions are expanded to contain more detailed information about the time, the user's location and aggregated statistics about the mean of the categories, location and interaction-strength of items with which the user has interacted with. Statistics are solely based on the training set. Values for unknown users are filled with the mean in the training data.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/learning_subsystem_position}}}
	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem. The dashed green lines indicate the mean, the straight orange lines the median. The percentage below each algorithm indicates how often it is the best possible algorithm. To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.}%
	\label{fig:MetaLearnerStatistics}
\end{figure}

>>>>

	\lstset{basicstyle=\ttfamily,breaklines=true}  % Prettier code highlighting style
	\pagestyle{empty}  % Prettier page format without header and footer

@@

\titlerunning{Augmenting the DonorsChoose.org Corpus for Meta-Learning}  % Abbreviated title
\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning%
	\thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}}
\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2} \and Joeran~Beel\inst{1,2}}
\authorrunning{G. Edenhofer et al.}  % Abbreviated author field
\institute{
	Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\ \and
	National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan\\ \email{beelj@tcd.ie, ancollin@tcd.ie, aizawa@nii.ac.jp}
}

\maketitle  % Typeset the header of the contribution
%\markboth{}{}  % Clear the section and author from the page header; also see `\pagestyle`

@@

Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way as to allow researchers to focus on the actual meta-learning task. We are augmenting a publicly available dataset intrinsically about recommendations which to our best knowledge has not been used for meta-learning before in the scientific community. Yet due to its feature-rich and vast corpus is a suitable candidate. The raw dataset is augmented with metadata of several machine learning algorithms from a variety of fields (cf.~\cite{DBLP:journals/corr/abs-1805-12118}). In place of a metric, the recall in a Top-N set is used as it can be computed for a wide range of algorithms. The dataset is further amended with aggregated statistics about users and items, and metadata of an exemplary experiment.

@@

\subsection{The Dataset}
DonorsChoose.org is an organization which enables teachers to file project requests for resources for their school. Collectively the nonprofit has raised $\$685$ million for classrooms in the United States of America. Their dataset composed of past donations features $4.69$ million transactions performed by $2.12$ million users having donated to $1.11$ million projects. This work uses the eighth version of the dataset hosted at \href{https://www.kaggle.com/donorschoose/io}{kaggle.com/donorschoose/io}. An exemplary itemized view of the augmented dataset is shown in~\autoref{tab:IllustrativeTable} with an outline of the plain data to the left of the separator.

@@

In a first step, we apply two collaborative filtering techniques and two content-based filtering techniques. The performance measures of the single algorithms are amended to the table. Next, we calculate aggregated user and item statistics and added them to the table. Lastly, four exemplary meta-learners are applied and the performance measures of the individual approaches are added to the corpus.

@@

Additionally, users having interacted less than twice are removed as well. Although, this limits the target group, the step is unavoidable as the employed validation process requires at least one interaction per user for testing and one for training. The evaluation requires user profiles and hence training-transactions in order to recommend new items which in turn need to be validated against test-transactions. Lastly, the donated amount is transformed to a transaction strength in the range of unity to five in analogy to a rating score. This step reduces the influence of outliers.

@@

The recall in a Top-N test set is used as score of how good an algorithm is able to recommend an item.
\begin{enumerate*}[label= (\arabic*)]
	\item For each user, first $100$ items with which the user has not interacted are selected.
	\item The algorithm is then requested to rank an item with which the user has interacted but which was not used for building the user's profile and the $100$ randomly sampled items. It is assumed that the random $100$ items are of low interest to the user.
	\item The position of the item with which the user has interacted in the ranked test set may now be taken as the recall in a Top-N test set.
\end{enumerate*}

@@

\subsection{Statistics and Application of the Learning Subsystem}
The meta-learning system processes the metadata of the learning subsystem and further statistics. Its performance is evaluated via a holdout split on the transaction table using $80\%$ for training and the rest for testing. Transactions are expanded to contain more detailed information about the time, the user's location and aggregated statistics about the mean of the categories, location and interaction-strength of items with which the user has interacted with. Statistics are solely based on the training set. Values for unknown users are filled with the mean in the training data.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/learning_subsystem_position}}}
	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem. The dashed green lines indicate the means, the straight orange lines the medians. The percentage below each algorithm indicates how often it is the best possible algorithm. To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.}%
	\label{fig:MetaLearnerStatistics}
\end{figure}

### 2019-04-10 doc/poster/main.tex
{paper,poster}/main.tex: Tweaks and suggestions

\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning}
\subject{Algorithm Selection and Meta-Learning in Information Retrieval}
\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2} \and Joeran~Beel\inst{1,2}}
\institute{%
	\inst{1}Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\
	\inst{2}National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan
	\and \href{mailto:beelj@tcd.ie}{beelj@tcd.ie}, \href{mailto:collinsa@tcd.ie}{collinsa@tcd.ie}, \href{mailto:aizawa@nii.ac.jp}{aizawa@nii.ac.jp}
}
\date{\itshape{} Algorithm Selection and Meta-Learning in Information Retrieval (AMIR)}  % Set date to venue

@@

				Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way as to allow researchers to focus on the actual meta-learning task. We are presenting a public domain dataset which to our best knowledge has not been used for meta-learning before in the scientific community, yet due to its feature-rich and vast corpus is suitable.
			\end{block}
		\end{column}

@@

		\begin{column}{0.45\textwidth}
			\begin{block}{Methodology}
				The DonorsChoose.org dataset is composed of past donations featuring $4.69$ million transactions performed by $2.12$ million users having donated to $1.11$ million projects. In contrast to, e.g., the popular MovieLense dataset, the DonorsChoose.org corpus provides significantly more transactions with more detailed item and transaction information as exemplary seen in~\autoref{tab:IllustrativeTable}.
				\parvspace{}

>>>>

\title{Augmenting the DonorsChoose.org Corpus for Meta-Learning}
\subject{Algorithm Selection and Meta-Learning in Information Retrieval}
\author{Gordian~Edenhofer\inst{1,2} \and Andrew~Collins\inst{1} \and Akiko~Aizawa\inst{2} \and Joeran~Beel\inst{1,2}}
\institute{%
	\inst{1}Trinity College Dublin, School of Computer Science \& Statistics, ADAPT Centre, Ireland\\
	\inst{2}National Institute of Informatics Tokyo, Digital Content and Media Sciences Division, Japan
	\and \href{mailto:beelj@tcd.ie}{beelj@tcd.ie}, \href{mailto:ancollin@tcd.ie}{ancollin@tcd.ie}, \href{mailto:aizawa@nii.ac.jp}{aizawa@nii.ac.jp}
}
\date{\itshape{} Algorithm Selection and Meta-Learning in Information Retrieval (AMIR)}  % Set date to venue

@@

				Our objective is to address the data augmentation part in a comprehensive and reproducible~\cite{UMUAI:TowardsReproducibilityInRecSysBeel2016} way. We are augmenting a public domain dataset intrinsically about recommendations which to our best knowledge has not been used for meta-learning before in the scientific community. Yet due to its feature-rich and vast corpus is suitable.
			\end{block}
		\end{column}

@@

		\begin{column}{0.45\textwidth}
			\begin{block}{Methodology}
				The DonorsChoose.org dataset is composed of past donations featuring $4.69$ million transactions performed by $2.12$ million users having donated to $1.11$ million projects. It provides more feature-richt transactions in contrast to, e.g., the popular MovieLens dataset as outlined in~\autoref{tab:IllustrativeTable}.
				\parvspace{}
